### 2020-02-02 thesis/paper.tex
fixes
structure

\subsubsection{Adding Methods}
To additional Methods they must be implemented using the corresponding interface and added to the class StartWindow. To add them to this class the static methods initGenerators(), initReducers() and initNormalizers() must add the new method to the list of methods. As an example adding a new generator (newGeneratorX) would require adding ``generators.add(new newGeneratorX());'' to the function initGenerators().

@@

\subsubsection{Adding Methods}

@@

\begin{itemize}
  \item Clustering Distance Measure: IMetaDistanceMeasure
\end{itemize}
\subsubsection{Clustering Distance Measure}
The interface IMetaDistanceMeasure is used to define distance measures that can be used for OPTICS for meta clustering. These distance measures should represent how different two clustering solutions are from each other while needing to fulfill the requirements of a metric. For a measure (indicated with $d(x,y)$) to be considered metric the following conditions must be met:
\begin{itemize}
  \item $d(x,y)\geq0$: distances must be non-negative
  \item $d(x,y)=0$ iff $x=y$: the distance between two objects is zero if and only if both objects are equal
  \item $d(x,y)=d(x,y)$: the distance must fulfill the symmetry condition
  \item $d(x,z)\leq d(x,y)+d(y,z)$: the triangle inequality must hold
\end{itemize}

The default implemented distance measures are Variation of Information and Clustering Error. 
%%more

@@

@@

\part{Testing}
\chapter{Experiments}\label{cha:experiments}
\section{Solutions unattainable from simple Clustering}
bla

>>>>

\subsubsection*{Adding Data Manipulation Methods}
To additional Methods they must be implemented using the corresponding interface and added to the class StartWindow. To add them to this class the static methods initGenerators(), initReducers() and initNormalizers() must add the new method to the list of methods. As an example adding a new generator (newGeneratorX) would require adding ``generators.add(new newGeneratorX());'' to the function initGenerators().

@@

\subsubsection*{Adding Clustering Algorithms}

@@

\begin{itemize}
  \item Clustering Distance Measure: IMetaDistanceMeasure
\end{itemize}
\subsubsection{Clustering Distance Measures}
The interface IMetaDistanceMeasure is used to define distance measures that can be used for OPTICS for meta clustering. These distance measures should represent how different two clustering solutions are from each other while needing to fulfill the requirements of a metric. For a distance measure, here indicated with $d(x,y)$ where $x$ and $y$ are objects, to be considered metric the following conditions must hold:
\begin{itemize}
  \item $d(x,y)\geq0$: distances must be non-negative
  \item $d(x,y)=0$ iff $x=y$: the distance between two objects is zero if and only if both objects are equal
  \item $d(x,y)=d(x,y)$: the distance must fulfill the symmetry condition
  \item $d(x,z)\leq d(x,y)+d(y,z)$: the triangle inequality must hold
\end{itemize}

The default implemented distance measures are Variation of Information and Clustering Error. 
%%more
\subsubsection*{Adding Distance Measures}
bla

@@

\subsubsection{Consensus Functions}
bla

\subsubsection*{Adding Consensus Functions}
bla

@@

\part{Testing}
\chapter{Experiments}\label{cha:experiments}
\section{Solutions better than Base-Clusterings}
bla
